KidsAIR: merge health datasets

### 2020-05-14 child_health_data_summary.Rmd
update analysis, results, manuscript tables

```{r}
# Load data
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
demographics_clean <- read_rds("Output/demographics_clean.rds")
pm_clean <- read_rds("Output/pm_clean.rds")

kids_med_visit <- read_rds("Output/kids_med_visit.rds") 
```

>>>>

```{r}
# Load data
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))
demographics_clean <- read_rds(paste0(file_path, "Output/demographics_clean.rds"))
pm_clean <- read_rds(paste0(file_path, "Output/pm_clean.rds"))

kids_med_visit <- read_rds(paste0(file_path, "Output/kids_med_visit.rds")) 
```

### 2020-05-14 exposure_covariate_associations.Rmd
update analysis, results, manuscript tables

  analysis_data <- dataset %>% 
    filter(winter_id == 1 & treatment == "Placebo") %>% 
    group_by(area, home) %>% 
    distinct(home, .keep_all = TRUE) %>% 
    rename(analysis_covar = covar) %>% 
    ungroup() %>% 
    select(pm_mean_sampling_period, analysis_covar)

>>>>

  analysis_data <- dataset %>% 
    filter(winter_id == 1 & treatment == "Placebo" & area == "WMT") %>% 
    group_by(area, home) %>% 
    distinct(home, .keep_all = TRUE) %>% 
    rename(analysis_covar = covar) %>% 
    ungroup() %>% 
    select(pm_mean_sampling_period, analysis_covar)

### 2020-05-14 exposure_models.Rmd
update analysis, results, manuscript tables

# Summary Statistics
missing_summary <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(stove_age_3level), "missing yes", "missing no")) %>%
  group_by(area, missing_var) %>% 
  summarize(n = n(),
            mean_pm = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_pm = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_pm = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  mutate(total_n = sum(n),
         perc_miss = n/total_n*100) %>% 
  select(area, missing_var, n, perc_miss, mean_pm, sd_pm, median_pm)
missing_summary

# T-tests
missing_test <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(stove_age_3level), "missing yes", "missing no")) %>% 
  filter(!is.na(log_pm_mean_sampling_period) & !is.na(missing_var))

@@

missing_summary <- complete_case %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_var = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_var = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_var = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_var, sd_var, median_var)
missing_summary

@@

missing_summary <- missing_data %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_var = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_var = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_var = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_var, sd_var, median_var)
missing_summary

@@

write_rds(imputed_data, paste0(file_path, "Output/imputed_exposure_data_7may2020.rds"))

imputed_exposure_data <- read_rds(paste0(file_path, "Output/imputed_exposure_data_7may2020.rds"))

@@

write_rds(model_ave, paste0(file_path, "Output/imputed_exposure_model_7may2020.rds"))

exposure_model <- read_rds(paste0(file_path, "Output/imputed_exposure_model_7may2020.rds"))

summary(test_model_results)

>>>>

# Summary Statistics
missing_summary <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(stove_grade_3level), "missing yes", "missing no")) %>%
  group_by(area, missing_var) %>% 
  summarize(n = n(),
            mean_pm = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_pm = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_pm = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  mutate(total_n = sum(n),
         perc_miss = n/total_n*100) %>% 
  select(area, missing_var, n, perc_miss, mean_pm, sd_pm, median_pm)
missing_summary

# T-tests
missing_test <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(stove_grade_3level), "missing yes", "missing no")) %>% 
  filter(!is.na(log_pm_mean_sampling_period) & !is.na(missing_var))

@@

missing_summary <- complete_case %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_var = mean(mean_temp_sampling_period_5, na.rm = TRUE), 
            sd_var = sd(mean_temp_sampling_period_5, na.rm = TRUE),
            median_var = median(mean_temp_sampling_period_5, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_var, sd_var, median_var)
missing_summary

@@

missing_summary <- missing_data %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_var = mean(mean_temp_sampling_period_5, na.rm = TRUE), 
            sd_var = sd(mean_temp_sampling_period_5, na.rm = TRUE),
            median_var = median(mean_temp_sampling_period_5, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_var, sd_var, median_var)
missing_summary

@@

write_rds(imputed_data, paste0(file_path, "Output/imputed_exposure_data_14may2020.rds"))

imputed_exposure_data <- read_rds(paste0(file_path, "Output/imputed_exposure_data_14may2020.rds"))

@@

write_rds(model_ave, paste0(file_path, "Output/imputed_exposure_model_14may2020.rds"))

exposure_model <- read_rds(paste0(file_path, "Output/imputed_exposure_model_14may2020.rds"))

summary(model_ave)

### 2020-05-14 home_char_act_summary.Rmd
update analysis, results, manuscript tables

```{r}
# Load dataset
home_char_clean <- read_rds("Output/home_char_clean.rds") 
home_act_clean <- read_rds("Output/home_act_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
#pm_clean <- read_rds("Output/pm_clean.rds")
```

>>>>

```{r}
# Load dataset
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

home_char_clean <- read_rds(paste0(file_path, "Output/home_char_clean.rds")) 
home_act_clean <- read_rds(paste0(file_path, "Output/home_act_clean.rds"))
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))
#pm_clean <- read_rds("Output/pm_clean.rds")
```

### 2020-05-14 manuscript_tables_figures.Rmd
update analysis, results, manuscript tables

---
title: 'KidsAIR: manuscript tables/figures'
author: "Ethan Walker"
date: "Started 13 May 2020, Updated 13 May 2020"
output:
  powerpoint_presentation: default
---

@@

num_funct_total("residents_under_five")
num_funct_area("residents_under_five")
num_funct_total("home_bedrooms")
num_funct_area("home_bedrooms")
```

>>>>

---
title: 'KidsAIR: manuscript tables/figures'
author: "Ethan Walker"
date: "Started 13 May 2020, Updated 14 May 2020"
output:
  powerpoint_presentation: default
---

@@

num_funct_total("residents_under_five")
num_funct_area("residents_under_five")
num_funct_total("home_bedrooms")
num_funct_area("home_bedrooms")
num_funct_total("pm_mean_sampling_period")
num_funct_area("pm_mean_sampling_period")
num_funct_total("pm_sample_interval")
num_funct_area("pm_sample_interval")
num_funct_total("moisture_closest")
num_funct_area("moisture_closest")
num_funct_total("temp_indoor_max")
num_funct_area("temp_indoor_max")
num_funct_total("rh_indoor_max")
num_funct_area("rh_indoor_max")
num_funct_total("mean_temp")
num_funct_area("mean_temp")
num_funct_total("amb_pm_24hr")
num_funct_area("amb_pm_24hr")
```

```{r}
other_vars_total <- exposure_analysis_data_short %>% 
  rename(new_var = home_act_sweep_sum) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
other_vars_total

other_vars_area <- exposure_analysis_data_short %>% 
  rename(new_var = home_act_sweep_sum) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  group_by(area) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
other_vars_area
```

### 2020-05-14 merge_datasets.Rmd
update analysis, results, manuscript tables

# Create new dataset with mean PM/SUMs; join with covariates
## Long data averaged over sampling date, including SUMs dates, repeated by child_id
```{r}
# Prep PM data to join with SUMs data by sampling day
pm_join <- pm_clean %>% 
  group_by(area, home) %>% 
  mutate(pm_mean_sampling_period = mean(pm, na.rm = TRUE)) %>% 
  group_by(area, home, sampling_day) %>% 
  mutate(pm_mean_sampling_day = mean(pm, na.rm = TRUE)) %>% 
  mutate(sample_datetime = ymd_hms(pm_datetime_new)) %>% 
  separate(sample_datetime, c("sample_date", "sample_time"), sep = " ",
           remove = FALSE) %>% 
  group_by(area, home, sample_date) %>% 
  mutate(pm_mean_daily = mean(pm, na.rm = TRUE),
         pm_daily_obs = n()) %>% 
  group_by(area, home, sampling_day) %>% 
  arrange(sample_datetime) %>% 
  mutate(pm_last_datetime = last(sample_datetime),
         pm_first_datetime = first(sample_datetime)) %>% 
  mutate(winter_id = as.character(winter_id)) %>% 
  ungroup() %>% 
  arrange(area, home, sample_date, desc(pm_spike_1000),
          desc(pm_spike_2000), desc(pm_spike_5000)) %>% 
  select(area, home, home_winter_id, winter_id, treatment, dtid, day_of_week, 
         pm_total_observations, pm_mean_sampling_period, sampling_day, 
         pm_mean_sampling_day, pm_first_datetime, pm_last_datetime,
         sample_date, pm_mean_daily, pm_daily_obs, pm_spike_1000,
         pm_spike_2000, pm_spike_5000) %>% 
  group_by(area, home) %>% 
  distinct(sample_date, .keep_all = TRUE) %>% 
  ungroup() %>% 
  arrange(area, home, sample_date)

@@

analysis_data2 <- demographics_clean %>% 
  full_join(analysis_data1, by = c("area", "home", "home_winter_id", 
                                    "winter_id", "treatment")) %>% 
  filter(!is.na(home_winter_id)) %>% 
  mutate(income_3level = fct_collapse(income,
                               "Less than $20,000" = "Less than $20,000",
                               "$20,000-$49,999" = 
                                 c("$20,000 to $29,999", "$30,000 to $39,999",
                                   "$40,000 to $49,999"),
                                "$50,000+" = 
                                 c("$50,000 to $74,999", "$75,000 to $99,999",
                                   "$100,000 or more")),
         income_3level = factor(income_3level, levels = c("Less than $20,000", 
                                            "$20,000-$49,999", 
                                            "$50,000+")), 
         education_3level = fct_collapse(education,
                                  "High school or less" = 
                                    c("Less than high school", 
                                      "High school diploma or GED"),
                                  "Some college" = "Some college",
                                  "College degree" = "College degree"),
         education_3level = factor(education_3level, levels = c("High school or less", 
                                            "Some college", 
                                            "College degree")), 
         race_parent_2level = fct_collapse(race_parent,
                                    "White" = "White",
                                    "Non-white" = 
                                      c("American Indian/Alaskan Native",
                                        "Asian", "More than one race")),
         race_parent_2level = factor(race_parent_2level, levels = c("White", "Non-white")), 
         total_residents_2level = fct_collapse(total_residents,
                                    "<5" = c("1", "2", "3", "4"),
                                    "5+" = c("5", "6", "7", "8", "9", "10",
                                             "11", "12", "13", "14", "15")),
         total_residents_2level = factor(total_residents_2level, levels = c("<5", "5+")),
         residents_under5_2level = fct_collapse(residents_under_five,
                                    "1" = c("0", "1"),
                                    "2+" = c("2", "3", "4", "5")),
         residents_under5_2level = factor(residents_under5_2level, levels = c("1", "2+"))) %>% 
  ungroup() %>% 
  arrange(area, home, home_winter_id, sample_date)

@@

#write_rds(analysis_data7, paste0(output_path, "Output/exposure_analysis_data_long.rds"))
#write_csv(analysis_data7, paste0(output_path, "Output/exposure_analysis_data_long.csv"))

@@

exposure_analysis_data_long_new <- exposure_analysis_data_long %>%
  # fix incorrect data after checking paper logs
  mutate(total_residents = if_else(home == "WMA438", "6", total_residents),
         total_residents = if_else(home == "WMA480" & winter_id == 1, "13", total_residents),
         total_residents_2level = fct_collapse(total_residents,
                                    "<5" = c("1", "2", "3", "4"),
                                    "5+" = c("5", "6", "7", "8", "9", "10",
                                             "11", "12", "13", "14")),
         total_residents_2level = factor(total_residents_2level, levels = c("<5", "5+")),
         income = as.character(income),
         income = if_else(home == "WMA480" & winter_id == 1, "$40,000 to $49,999", income),
         income_3level = fct_collapse(income,
                               "Less than $20,000" = "Less than $20,000",
                               "$20,000-$49,999" = 
                                 c("$20,000 to $29,999", "$30,000 to $39,999",
                                   "$40,000 to $49,999"),
                                "$50,000+" = 
                                 c("$50,000 to $74,999", "$75,000 to $99,999",
                                   "$100,000 or more")),
         income_3level = factor(income_3level, levels = c("Less than $20,000", 
                                            "$20,000-$49,999", 
                                            "$50,000+"))) %>% 
  ungroup() %>% 
  left_join(kids_amb_pm_data, by = c("area", "home", "sample_date")) %>% 
  select(-zip, -lat_home, -long_home) %>% 
  left_join(kids_amb_temp_data, by = c("area", "home", "sample_date")) %>%
  arrange(area, home, home_winter_id, sample_date)

#write_rds(exposure_analysis_data_long_new, paste0(output_path, "Output/exposure_analysis_data_long_new.rds"))
#write_csv(exposure_analysis_data_long_new, paste0(output_path, "Output/exposure_analysis_data_long_new.csv"))
```

# Convert long data to medium: only keeping days with PM sampling, repeated by child_id
```{r}
exposure_analysis_data_long_new <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_long_new.rds"))

@@

#write_rds(exposure_analysis_data_medium, paste0(output_path, "Output/exposure_analysis_data_medium.rds"))
#write_csv(exposure_analysis_data_medium, paste0(output_path, "Output/exposure_analysis_data_medium.csv"))
```

# Convert medium data to short: only keeping 1 observation per sampling period, repeated by child_id
```{r}
exposure_analysis_data_medium <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_medium.rds"))
exposure_analysis_data_long <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_long_new.rds")) 
sums_rolling_pm_data <- 
  read_rds(paste0(output_path, "Output/sums_rolling_pm_data.rds"))

@@

#write_rds(exposure_analysis_data_short, paste0(output_path, "Output/exposure_analysis_data_short.rds"))
#write_csv(exposure_analysis_data_short, paste0(output_path, "Output/exposure_analysis_data_short.csv"))
```

@@

#write_rds(pm_sums_joined3, paste0(output_path, "Output/sums_rolling_pm_data.rds"))
#write_csv(pm_sums_joined3, paste0(output_path, "Output/sums_rolling_pm_data.csv"))
```

>>>>

# Create new dataset with mean PM/SUMs; join with covariates
## Long data averaged over sampling date, including SUMs dates, repeated by child_id
```{r}
# Prep PM data to join with SUMs data by sampling day
pm_join <- pm_clean %>% 
  group_by(area, home) %>% 
  mutate(pm_mean_sampling_period = mean(pm, na.rm = TRUE)) %>% 
  group_by(area, home, sampling_day) %>% 
  mutate(pm_mean_sampling_day = mean(pm, na.rm = TRUE)) %>% 
  mutate(sample_datetime = ymd_hms(pm_datetime_new)) %>% 
  separate(sample_datetime, c("sample_date", "sample_time"), sep = " ",
           remove = FALSE) %>% 
  group_by(area, home, sample_date) %>% 
  mutate(pm_mean_daily = mean(pm, na.rm = TRUE),
         pm_daily_obs = n()) %>% 
  group_by(area, home, sampling_day) %>% 
  arrange(sample_datetime) %>% 
  mutate(pm_last_datetime = last(sample_datetime),
         pm_first_datetime = first(sample_datetime)) %>% 
  mutate(winter_id = as.character(winter_id)) %>% 
  ungroup() %>% 
  arrange(area, home, sample_date, desc(pm_spike_1000),
          desc(pm_spike_2000), desc(pm_spike_5000)) %>% 
  select(area, home, home_winter_id, winter_id, treatment, dtid, day_of_week, 
         pm_total_observations, pm_mean_sampling_period, sampling_day, 
         pm_mean_sampling_day, pm_first_datetime, pm_last_datetime,
         sample_date, pm_mean_daily, pm_daily_obs, pm_spike_1000,
         pm_spike_2000, pm_spike_5000, pm_sample_interval) %>% 
  group_by(area, home) %>% 
  distinct(sample_date, .keep_all = TRUE) %>% 
  ungroup() %>% 
  arrange(area, home, sample_date)

@@

analysis_data2 <- demographics_clean %>% 
  mutate(residents_under_five = if_else(residents_under_five == 0 & age_child_nov != 4, "NA", residents_under_five),
         residents_under_five = if_else(residents_under_five == 0 & child_id_char == "WMA673B", "NA", residents_under_five)) %>% 
  replace_with_na(replace = list(total_residents = "0")) %>% 
  replace_with_na(replace = list(total_residents = "1")) %>% 
  replace_with_na(replace = list(residents_under_five = "NA")) %>% 
  full_join(analysis_data1, by = c("area", "home", "home_winter_id", 
                                    "winter_id", "treatment")) %>% 
  filter(!is.na(home_winter_id)) %>% 
  mutate(income_3level = fct_collapse(income,
                               "Less than $20,000" = "Less than $20,000",
                               "$20,000-$49,999" = 
                                 c("$20,000 to $29,999", "$30,000 to $39,999",
                                   "$40,000 to $49,999"),
                                "$50,000+" = 
                                 c("$50,000 to $74,999", "$75,000 to $99,999",
                                   "$100,000 or more")),
         income_3level = factor(income_3level, levels = c("Less than $20,000", 
                                            "$20,000-$49,999", 
                                            "$50,000+")), 
         education_3level = fct_collapse(education,
                                  "High school or less" = 
                                    c("Less than high school", 
                                      "High school diploma or GED"),
                                  "Some college" = "Some college",
                                  "College degree" = "College degree"),
         education_3level = factor(education_3level, levels = c("High school or less", 
                                            "Some college", 
                                            "College degree")), 
         race_parent_2level = fct_collapse(race_parent,
                                    "White" = "White",
                                    "Non-white" = 
                                      c("American Indian/Alaskan Native",
                                        "Asian", "More than one race")),
         race_parent_2level = factor(race_parent_2level, levels = c("White", "Non-white")), 
         total_residents_2level = fct_collapse(total_residents,
                                    "<5" = c("1", "2", "3", "4"),
                                    "5+" = c("5", "6", "7", "8", "9", "10",
                                             "11", "12", "13", "14", "15")),
         total_residents_2level = factor(total_residents_2level, levels = c("<5", "5+")),
         residents_under5_2level = fct_collapse(residents_under_five,
                                    "1" = c("0", "1"),
                                    "2+" = c("2", "3", "4", "5")),
         residents_under5_2level = factor(residents_under5_2level, levels = c("1", "2+"))) %>% 
  ungroup() %>% 
  arrange(area, home, home_winter_id, sample_date)

@@

write_rds(analysis_data7, paste0(output_path, "Output/exposure_analysis_data_long.rds"))
write_csv(analysis_data7, paste0(output_path, "Output/exposure_analysis_data_long.csv"))

@@

exposure_analysis_data_long_new <- exposure_analysis_data_long %>%
  # fix incorrect data after checking paper logs
  mutate(total_residents = if_else(home == "WMA438", "6", total_residents),
         total_residents = if_else(home == "WMA480" & winter_id == 1, "13", total_residents),
         total_residents_2level = fct_collapse(total_residents,
                                    "<5" = c("2", "3", "4"),
                                    "5+" = c("5", "6", "7", "8", "9", "10",
                                             "11", "12", "13", "14")),
         total_residents_2level = factor(total_residents_2level, levels = c("<5", "5+")),
         income = as.character(income),
         income = if_else(home == "WMA480" & winter_id == 1, "$40,000 to $49,999", income),
         income_3level = fct_collapse(income,
                               "Less than $20,000" = "Less than $20,000",
                               "$20,000-$49,999" = 
                                 c("$20,000 to $29,999", "$30,000 to $39,999",
                                   "$40,000 to $49,999"),
                                "$50,000+" = 
                                 c("$50,000 to $74,999", "$75,000 to $99,999",
                                   "$100,000 or more")),
         income_3level = factor(income_3level, levels = c("Less than $20,000", 
                                            "$20,000-$49,999", 
                                            "$50,000+"))) %>% 
  ungroup() %>% 
  left_join(kids_amb_pm_data, by = c("area", "home", "sample_date")) %>% 
  select(-zip, -lat_home, -long_home) %>% 
  left_join(kids_amb_temp_data, by = c("area", "home", "sample_date")) %>%
  arrange(area, home, home_winter_id, sample_date)

write_rds(exposure_analysis_data_long_new, paste0(output_path, "Output/exposure_analysis_data_long_new.rds"))
write_csv(exposure_analysis_data_long_new, paste0(output_path, "Output/exposure_analysis_data_long_new.csv"))
```

# Convert long data to medium: only keeping days with PM sampling, repeated by child_id
```{r}
output_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

@@

write_rds(exposure_analysis_data_medium, paste0(output_path, "Output/exposure_analysis_data_medium.rds"))
write_csv(exposure_analysis_data_medium, paste0(output_path, "Output/exposure_analysis_data_medium.csv"))
```

# Convert medium data to short: only keeping 1 observation per sampling period, repeated by child_id
```{r}
output_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

exposure_analysis_data_medium <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_medium.rds"))
exposure_analysis_data_long <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_long_new.rds")) 
sums_rolling_pm_data <- 
  read_rds(paste0(output_path, "Output/sums_rolling_pm_data.rds"))

@@

write_rds(exposure_analysis_data_short, paste0(output_path, "Output/exposure_analysis_data_short.rds"))
write_csv(exposure_analysis_data_short, paste0(output_path, "Output/exposure_analysis_data_short.csv"))
```

@@

write_rds(pm_sums_joined3, paste0(output_path, "Output/sums_rolling_pm_data.rds"))
write_csv(pm_sums_joined3, paste0(output_path, "Output/sums_rolling_pm_data.csv"))
```

### 2020-05-14 merge_health_datasets.Rmd
update analysis, results, manuscript tables

---
title: "KidsAIR: merge health datasets"
author: "Ethan Walker"
date: "Started 27 March 2020, Updated 22 April 2020"
output: pdf_document
---

@@

#write_rds(health_merged6, paste0(output_path, "Output/health_data_merged.rds"))
#write_csv(health_merged6, paste0(output_path, "Output/health_data_merged.csv"))
```

>>>>

---
title: "KidsAIR: merge health datasets"
author: "Ethan Walker"
date: "Started 27 March 2020, Updated 14 May 2020"
output: pdf_document
---

@@

write_rds(health_merged6, paste0(output_path, "Output/health_data_merged.rds"))
write_csv(health_merged6, paste0(output_path, "Output/health_data_merged.csv"))
```
